\lhead{\emph{Acrónimos}}  % Set the left side page header to "Symbols"
\chapter*{Lista de Acrónimos\hfill}
\begin{abbreviations}
    \item[ACS] \textbf{A}nt \textbf{C}olony \textbf{S}ystem.
    \item[API] \textbf{A}pplication \textbf{P}rogramming \textbf{I}nterface.
    \item[ATSP] \textbf{A}symmetric \textbf{T}ravelling \textbf{S}ales \textbf{P}roblem.
    \item[BD] \textbf{B}ase de \textbf{D}atos.
    \item[BSA] \textbf{B}acktracking \textbf{S}earch \textbf{A}lgorithm.
    \item[CAD] \textbf{C}omputer-\textbf{A}ided \textbf{D}esign.
    \item[CARP] \textbf{C}apacitated \textbf{A}rc \textbf{R}outing \textbf{P}roblem.
    \item[CPP] \textbf{C}hinese \textbf{P}ostman \textbf{P}roblem.
    \item[CRS] \textbf{C}oordinate \textbf{R}eference \textbf{S}ystem.
    \item[CVRP] \textbf{C}apacitated \textbf{V}ehicle \textbf{R}outing \textbf{P}roblem.
    \item[DER] \textbf{D}iagrama \textbf{E}ntidad \textbf{R}elación.
    \item[DSU] \textbf{D}irección de \textbf{S}ervicios \textbf{U}rbanos.
    \item[EPSG] \textbf{E}uropean \textbf{P}etroleum \textbf{S}urvey \textbf{G}roup.
    \item[GA] \textbf{G}enetic \textbf{A}lgorithm.
    \item[GDRPP] \textbf{G}eneralized \textbf{D}irected \textbf{R}ural \textbf{P}ostman \textbf{P}roblem.
    \item[GIS] \textbf{G}eographical \textbf{I}nformation \textbf{S}ystem.
    \item[GPS] \textbf{G}lobal \textbf{P}ositioning \textbf{S}ystem.
    \item[SGBG] \textbf{S}istemas de \textbf{G}estión de \textbf{B}ase de \textbf{D}atos.
    \item[ID] \textbf{ID}entificador.
    \item[IP] \textbf{I}nteger \textbf{P}rogramming.
    \item[JSON] \textbf{J}ava\textbf{S}cript \textbf{O}bject \textbf{N}otation.
    \item[JWT] \textbf{J}SON \textbf{W}eb \textbf{T}okens.
    \item[LP] \textbf{L}inear \textbf{P}rogramming.
    \item[MDA] \textbf{M}unicipalidad \textbf{D}e \textbf{A}sunción.
    \item[MILP] \textbf{M}ixed \textbf{I}nteger \textbf{L}inear \textbf{P}rogramming.
    \item[MM] \textbf{M}ap \textbf{M}atching.
    \item[MOPC] \textbf{M}inisterio de \textbf{O}bras \textbf{P}úblicas y \textbf{C}omunicaciones.
    \item[MVC] \textbf{M}odel \textbf{V}iew \textbf{C}ontroller.
    \item[ODbL] \textbf{O}pen \textbf{D}ata\textbf{b}ase \textbf{L}icense.
    \item[OGC] \textbf{O}pen \textbf{G}eospatial \textbf{C}onsortium.
    \item[OPL] \textbf{O}ptimization \textbf{P}rogramming \textbf{L}anguage.
    \item[OSM] \textbf{O}pen\textbf{S}treet\textbf{M}ap.
    \item[PCARP] \textbf{P}eriodic \textbf{C}apacitated \textbf{A}rc \textbf{R}outing \textbf{P}roblem.
    \item[SA] \textbf{S}imulated \textbf{A}nnealing.
    \item[SIG] \textbf{S}istema de \textbf{I}nformación \textbf{G}eográfica.
    \item[SWC] \textbf{S}olid \textbf{W}aste \textbf{C}ollection.    
    \item[SWM] \textbf{S}olid \textbf{W}aste \textbf{M}anagement.
    \item[RFID] \textbf{R}adio \textbf{F}recuency \textbf{ID}entification.
    \item[RPP] \textbf{R}ural \textbf{P}ostman \textbf{P}roblem.
    \item[SNC] \textbf{S}ervicio \textbf{N}acional de \textbf{C}atastro.
    \item[SRC] \textbf{S}istema de \textbf{R}eferencia de \textbf{C}oordenadas.
    \item[SRID] \textbf{S}patial \textbf{R}eference System \textbf{ID}entifier.
    \item[TIN] \textbf{T}riangulated \textbf{I}rregular \textbf{N}etwork.
    \item[TMS] \textbf{T}ile \textbf{M}ap \textbf{S}ervice.
    \item[TSP] \textbf{T}ravelling \textbf{S}ales \textbf{P}roblem.
    \item[TWL] \textbf{T}hreshold \textbf{W}aste \textbf{L}evel.
    \item[UTM] \textbf{U}niversal \textbf{T}ransverse \textbf{M}ercator.
    \item[VRP] \textbf{V}ehicle \textbf{R}outing \textbf{P}roblem.
    \item[VRPTW] \textbf{V}ehicle \textbf{R}outing \textbf{P}roblem with \textbf{T}ime \textbf{W}indow.
    \item[WCS] \textbf{W}eb \textbf{C}overage \textbf{S}ervice.
    \item[WFS] \textbf{W}eb \textbf{F}eature \textbf{S}ervice.
    \item[WGS84] \textbf{W}orld \textbf{G}eodetic \textbf{S}ystem 1984.
    \item[WMS] \textbf{W}eb \textbf{M}ap \textbf{S}ervice.
    \item[WMTS] \textbf{W}eb \textbf{M}ap \textbf{T}ile \textbf{S}ervice.
    \item[WSGI] \textbf{W}eb \textbf{S}erver \textbf{G}ateway \textbf{I}nterface.
    % \item[MVT] \textbf{M}apbox \textbf{V}ector \textbf{T}iles.
    % \item[ISO] \textbf{I}nternational \textbf{O}rganization for \textbf{S}tandardization.
\end{abbreviations}